Supplementary Materials for Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-24 analysis/supplementary materials/Supplementary Materials.Rmd
include equivalence test plots in supplementary materials

load(
  system.file(
    "extdata",
    "m_h1.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h1_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h2.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h2_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
```

@@

```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE}
p <- plot(equivalence_test(m_f1))

@@

```{r journal-code, echo=FALSE}
m_f1_report %>% 
  pander()
```

@@

```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE}
p <- plot(equivalence_test(m_f2))

@@

```{r journal-data, echo=FALSE}
m_f2_report %>% 
  pander()
```

@@

```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE}
p <- plot(equivalence_test(m_g1))

@@

```{r year-code, echo=FALSE}
m_g1_report %>% 
  pander()
```

@@

```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE}
p <- plot(equivalence_test(m_g2))

@@

```{r year-data, echo=FALSE}
m_g2_report %>% 
  pander()
```

@@

```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE}
p <- plot(equivalence_test(m_h1))

@@

```{r if5yr-code, echo=FALSE}
m_h1_report %>% 
  pander()
```

@@

```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE}
p <- plot(equivalence_test(m_h2))

@@

```{r if5yr-data, echo=FALSE}
m_h2_report %>% 
  pander()
```

@@

```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_f1_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption("")
```

@@

```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_f2_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption("")
```

@@

```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_g1_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption("")
```

@@

```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_g2_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption("")
```

@@

```{r if-5yr-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_h1_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption("")
```

@@

```{r if-5yr-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_h2_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption("")
```

>>>>

load(
  system.file(
    "extdata",
    "m_h1.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h1_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h2.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h2_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)

knitr::opts_chunk$set(
  fig.cap.pre = "Figure S",
  tab.cap.pre = "Table S"
)

```

@@

```{r journal-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability."}
p <- plot(equivalence_test(m_f1))

@@

@@

```{r journal-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal on articles\' supporting code availability."}
p <- plot(equivalence_test(m_f2))

@@

@@

```{r year-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication title on articles\' supporting code availability."}
p <- plot(equivalence_test(m_g1))

@@

@@

```{r year-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
p <- plot(equivalence_test(m_g2))

@@

@@

```{r if5yr-code-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the publishing journal's five-year impact factor on articles\' supporting code availability."}
p <- plot(equivalence_test(m_h1))

@@

@@

```{r if5yr-data-test, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Equivalence test for a model testing the effect of the year of publication on articles\' supporting data availability."}
p <- plot(equivalence_test(m_h2))

@@

@@

```{r effects-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_f1_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption("Full description of model fit for the effect of journal title on code availability. We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation). The model included assignee as random effect (formula: ~1 | assignee). Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions.")

```

@@

```{r effects-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_f2_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
    set_caption("Full description of model fit for the effect of journal title on data availability. We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with abbreviation (formula: comp_mthds_avail ~ abbreviation). The model included assignee as random effect (formula: ~1 | assignee). Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00) and student_t (location = 0.00, scale = 2.50) distributions.")

```

@@

```{r year-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_g1_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>%
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>%
  colformat_double(digits = 2) %>%
  set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption(
    "Full description of model fit for the effect of year of publication on code availability. We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year). The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)). Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
  )
```

@@

```{r year-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_g2_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>% 
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>% 
  colformat_double(digits = 2) %>% 
    set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
    set_caption("Full description of model fit for the effect of year of publication on data availability. We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year). The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)). Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions.")

```

@@

```{r if-5yr-analysis-code, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_h1_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>%
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>%
  colformat_double(digits = 2) %>%
  set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption(
    "Full description of model fit for the effect of five-year impact factor on code availability. We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year). The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)). Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
  )

```

@@

```{r if-5yr-analysis-data, echo=FALSE, message=FALSE, warning=FALSE}
as_tibble(m_h2_report) %>%
  filter(!grepl("Intercept", Parameter)) %>%
  filter(!grepl("R2", Parameter)) %>%
  filter(!is.na(Parameter)) %>%
  rename("ROPE %" = "ROPE_Percentage",
         "CI\nLow" = "CI_low",
         "CI\nHigh" = "CI_high") %>%
  flextable() %>%
  fontsize(size = 8, part = "all") %>%
  colformat_double(digits = 2) %>%
  set_formatter(
    `ROPE %` = function(x)
      ifelse((!is.na(x)), sprintf("%1.f%%", x * 100), x)
  ) %>%
  autofit() %>%
  set_caption(
    "Full description of model fit for the effect of five year impact factor on data availability. We fitted a Bayesian logistic mixed model (estimated using MCMC sampling with 4 chains of 10000 iterations and a warmup of 5000) to predict comp_mthds_avail with year (formula: comp_mthds_avail ~ year). The model included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)). Priors over parameters were set as normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), normal (mean = 0.00, SD = 1.00), student_t (location = 0.00, scale = 2.50) and student_t (location = 0.00, scale = 2.50) distributions."
  )
```
